%signal path for graphics files
\graphicspath{{img/}}







%==============================



\appendix
%-----
\section{\bibliographyname}
\newlist{bib}{enumerate}{1}%
\setlist[bib]{label={[\arabic*]},leftmargin=*}%

\subsection*{1.08 Published scientific conference contributions}
\begin{bib}
\item M. Petroni, L. Canciani, M. Mraz, M. Mo\v{s}kon, A qualitative method for parameter estimation in gene regulatory networks using extended Kalman filtering, \emph{Proceedings of 21st Electrotechnical and Computer Science Conference (ERK 2012)}, 39-42, 2012
\end{bib}

\subsection*{1.16 Independent scientific component part or a chapter in a monograph}
\begin{bib}[resume]
\item M. Mo\v{s}kon, J. Bordon, M. Mraz, N. Zimic, M. Petroni, \emph{Computational approaches in synthetic and systems biology}, accepted chapter for book Recent Advances in System Biology, edited by prof. A. Valente, prof. Y. Gao and prof. A. Sarkar, Nova Science Publishers Inc., USA, expected release September, 2013
\end{bib}

\subsection*{2.11 Undergraduate thesis}
\begin{bib}[resume]
\item Petroni M., \textit{Gene regulatory networks as dataflow processing platforms: BSc thesis}, Ljubljana, 2011
\end{bib}

\subsection*{2.24 Patent}
\begin{bib}[resume]
\item JERALA, Roman, AVBELJ, Monika, BEN\v{C}INA, Mojca, MORI, Jer\-neja, GABER, Rok, KOPRIVNJAK, Toma\v{z}, ANDERLUH, Gregor, VOVK, Irena, LEBAR, Tina, TURN\v{S}EK, Jernej, ILC, Tina, TOM\v{S}I\v{C}, Nejc, STO\v{S}ICKI, Tja\v{s}a, \v{Z}NIDARI\v{C}, Matej, BORDON, Jure, PETRO\-NI, Mattia, GLAVNIK, Vesna. Improved synthesis of biosynthetic product by ordered assembly of biosynthetic enzymes guided by the nucleotide sequence motif template: patent: SI 23510 (A), 2012-04-30. Ljubljana: Urad Republike Slovenije za intelektualno lastnino, 2012. 100 str., ilustr. [COBISS.SI-ID 4959514]
\end{bib}

\subsection*{3.25 Other performed works}
\begin{bib}[resume]
\item  ILC, Tina, LEBAR, Tina, STO\v{S}ICKI, Tja\v{s}a, TOM\-\v{S}I\v{C}, Nejc, TURN\-\v{S}EK, Jernej, \v{Z}NIDARI\v{C}, Matej, BORDON, Jure, \v{C}E\v{S}NOVAR, Rok, PE\-TRO\-NI, Mattia, PUSTOSLEM\v{S}EK, Rok. \emph{Competition team members: DNA coding beyond triplets}: grand prize winners at the International Genetically Engineered Machine competition - iGEM project 2010, Cambridge, Massachusetts Institute of Technology, November 2010, http://2010.igem.org/Team:Slovenia. [COBISS.SI-ID 4757018]
\end{bib}
